### 2015-11-23 paper.tex
add new rate table

		A detailed detector simulation software has been implemented based on Geant4. For each material in JUNO detector, 
		the radioactivity listed in table 2 are used in detector simulation to study its events rate.
		The results with different trigger thresholds are summarized in table 3, the multiplicity trigger is used as default.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1}  The inner singles rates} 
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c c c}
			\toprule  Singles Rate(Hz)&LS &Glass &Acrylic  &Steel &Copper &Rn &Rock  &Sum \\
			\hline
			E$>$0.7MeV &2.39   &2.43  &69.23  &0.89  &0.82 &15.94 &7.42     &99.12   \\
			E$>$0.6MeV &4.26   &2.66  &75.26  &0.95  &0.94 &19.79 &8.1223   &111.982 \\
			E$>$0.5MeV &12.06  &2.83  &81.49  &0.98  &1.06 &23.36 &8.6414   &130.421 \\
			E$>$0.4MeV &13.86  &3.24  &87.84  &1.22  &1.29 &26.11 &9.89333  &143.453 \\
			E$>$0.3MeV &15.51  &3.72  &98.57  &1.57  &1.51 &31.60 &11.359   &163.839 \\
			E$>$0.2MeV &17.16  &4.12  &117.33 &1.80  &1.89 &39.85 &12.5804  &194.73  \\
			E$>$0.1MeV &352.36 &5.27  &149.26 &2.22  &2.60 &54.97 &16.0919  &582.772 \\
			\bottomrule
		\end{tabular*}
	\end{center}
	\begin{multicols}{2}

		The events rate increases when the trigger threshold discreases. For a normal threshold of 0.5 MeV, the total events rate is about 130 Hz.
		Acrylic and Radon in water are two major sources of events. For radioactivity in LS, the events rate is suddenly changed from 17 Hz to 352 Hz.
		It is caused by $^{14}$C in LS generated by cosmic muons. $^{14}$C goes through radioactive beta decay by emitting an electron and an electron antineutrino.
		The emitted electrons have a maximum energy of 0.156 MeV and can not be triggered with 0.2 MeV threshold. 
		While, a fraction of $^{14}$C can be triggered by 0.1 MeV threshold.

@@

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The sum radioactivity singles rates in central detector on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  Sum Radioactivity Single Rate(Hz)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline
			%rate with out rock rateR$<$10m &142.368  &98.332  &96.9047 &95.9515 &95.2811  &93.7126 \\
			%			R$<$11m &153.808  &99.1398 &97.5285 &96.4432 &95.6678  &93.8127 \\
			%			R$<$12m &199.79   &102.354 &100.039 &98.4438 &97.2644  &94.2101 \\
			%			R$<$13m &249.897  &105.33  &102.395 &100.341 &98.7855  &94.5798 \\
			%			R$<$14m &249.897  &105.33  &102.395 &100.341 &98.7855  &94.5798 \\
			%			R$<$15m &289.921  &112.385 &107.156 &103.627 &101.128  &95.4422 \\
			%			R$<$16m &458.269  &148.923 &131.168 &119.73  &112.381  &99.866  \\
			%			R$<$17m &540.865  &173.071 &146.688 &129.847 &119.277  &102.776 \\
			R$<$10m &146.299  &104.685  &103.623  &102.569  &101.594  &100.510  \\  
			R$<$11m &158.055  &105.545  &104.290  &103.094  &102.007  &100.617  \\
			R$<$12m &205.307  &108.967  &106.975  &105.233  &103.709  &101.043  \\
			R$<$13m &256.797  &112.135  &109.494  &107.261  &105.331  &101.440  \\
			R$<$14m &256.797  &112.135  &109.494  &107.261  &105.331  &101.440  \\
			R$<$15m &297.926  &119.646  &114.585  &110.774  &107.829  &102.365  \\
			R$<$16m &470.923  &158.544  &140.262  &127.987  &119.827  &107.109  \\
			R$<$17m &555.812  &184.252  &156.858  &138.802  &127.180  &110.231  \\

>>>>

		A detailed detector simulation software has been implemented based on Geant4. For each material in JUNO detector, 
		the radioactivity listed in table 2 are used in detector simulation to study its events rate.
		The results with different trigger thresholds are summarized in table 3, the multiplicity trigger is used as default, the trigger time window is 300ns.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1}  The inner singles rates with 300ns trigger time window} 
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c c c}
			\toprule  Singles Rate(Hz)&LS &Glass &Acrylic  &Steel &Copper &Rn &Rock  &Sum \\
			\hline
			E$>$0.7MeV &12.92   &3.24      &75.61   &0.96   &0.98 &25.42   &9.12   &128.25    \\
			E$>$0.6MeV &15.01   &3.56      &85.23   &1.19   &1.23 &29.55   &10.21  &145.98    \\
			E$>$0.5MeV &16.59   &3.91      &99.77   &1.62   &1.57 &35.87   &12.98  &172.31    \\
			E$>$0.4MeV &69.10   &4.64      &126.76  &1.91   &2.09 &45.76   &18.32  &268.58    \\
			E$>$0.3MeV &1494.47 &10.27     &182.80  &2.97   &3.38 &69.53   &23.64  &1787.06   \\
			E$>$0.2MeV &3270.20 &191012.24 &1413.36 &99.23  &7.45 &1603.34 &131.34 &197537.16 \\
			E$>$0.1MeV &3275.50 &191113.60 &1436.98 &103.41 &8.61 &1607.81 &136.32 &197682.23 \\

		Because of dark noise, the events rate is very large when trigger thershold below 0.4MeV. If 
		we can shorten the trigger time window, there will be few dark noise in the trigger time window.
		In table 4, we show the results with 50ns trigger time window. We will discuss the method that 
		how to shorten the trigger time window at 4.4 section.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1}  The inner singles rates with 50ns trigger time window} 
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c c c}
			\toprule  Singles Rate(Hz)&LS &Glass &Acrylic  &Steel &Copper &Rn &Rock  &Sum \\
			\hline
			E$>$0.7MeV &4.40    &2.69      &59.52    &0.61     &0.69     &19.65    &7.12     &94.68   \\
			E$>$0.6MeV &10.32   &2.85      &67.08    &0.87     &0.82     &22.54    &8.31     &112.79  \\
			E$>$0.5MeV &13.09   &3.24      &75.87    &0.97     &0.99     &25.56    &9.27     &128.99  \\
			E$>$0.4MeV &15.09   &3.62      &85.63    &1.24     &1.25     &29.68    &10.52    &147.03  \\
			E$>$0.3MeV &16.64   &3.91      &100.12   &1.58     &1.57     &36.14    &13.25    &173.21  \\
			E$>$0.2MeV &61.59   &4.86      &127.16   &1.91     &2.12     &46.31    &17.45    &261.40  \\
			E$>$0.1MeV &1489.15 &14.58     &180.12   &2.63     &3.32     &71.32    &24.74    &1785.86 \\

		The events rate increases when the trigger threshold discreases. For a normal threshold of 0.5 MeV, the total events rate is about 129 Hz.
		Acrylic and Radon in water are two major sources of events. For radioactivity in LS, the events rate is suddenly changed from 16.6 Hz to 1489.15 Hz.
		It is caused by $^{14}$C in LS generated by cosmic muons. $^{14}$C goes through radioactive beta decay by emitting an electron and an electron antineutrino.
		The emitted electrons have a maximum energy of 0.156 MeV and can not be triggered with 0.2 MeV threshold. 
		While, a fraction of $^{14}$C can be triggered by 0.1 MeV threshold.

@@

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The sum radioactivity singles rates in central detector on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  Sum Radioactivity Single Rate(Hz)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline
			%rate with out rock rateR$<$10m &142.368  &98.332  &96.9047 &95.9515 &95.2811  &93.7126 \\
			%			R$<$11m &153.808  &99.1398 &97.5285 &96.4432 &95.6678  &93.8127 \\
			%			R$<$12m &199.79   &102.354 &100.039 &98.4438 &97.2644  &94.2101 \\
			%			R$<$13m &249.897  &105.33  &102.395 &100.341 &98.7855  &94.5798 \\
			%			R$<$14m &249.897  &105.33  &102.395 &100.341 &98.7855  &94.5798 \\
			%			R$<$15m &289.921  &112.385 &107.156 &103.627 &101.128  &95.4422 \\
			%			R$<$16m &458.269  &148.923 &131.168 &119.73  &112.381  &99.866  \\
			%			R$<$17m &540.865  &173.071 &146.688 &129.847 &119.277  &102.776 \\
			R$<$10m &257.962   &104.384  &100.144  &98.753   &97.392   &96.637   \\  
			R$<$11m &298.649   &105.884  &100.953  &99.373   &97.845   &96.788   \\
			R$<$12m &462.184   &111.851  &104.211  &101.898  &99.710   &97.388   \\
			R$<$13m &640.386   &117.375  &107.268  &104.293  &101.488  &97.947   \\
			R$<$14m &640.386   &117.375  &107.268  &104.293  &101.488  &97.947   \\
			R$<$15m &782.729   &130.472  &113.445  &108.441  &104.226  &99.249   \\
			R$<$16m &1381.456  &198.301  &144.602  &128.767  &117.378  &105.929  \\
			R$<$17m &1675.249  &243.129  &164.739  &141.538  &125.437  &110.325  \\
